A generalized definition of multidimensional item response theory parameters

### 2024-07-05 output/paper_draft/paper_M2PLM_parameters.Rmd
Updates "properties" section
After the addition to the "covariance-based version" section, the "properties" section must be updated to refer to those previous contents.

>>>>

We have seen how the two new versions of the parameters fulfill
the three conditions proposed by @reckase_discriminating_1991
for valid generalizations of the IRT parameters to the multidimensional case,
being the scale invariance of the $`r MDISC_COV_PARAM`$ the only exception.
We will consider now two more properties,
related to each of the two components of the $`r MIL_PARAM`$ parameter,
namely, the distance to the origin, and the measurement direction.
